---
title: "Education Project Midpoint Deliverable"
author: "Ian, Brenda, Leon, Jerry, Nicole"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("knitr")
library("dplyr")
source("scripts/summary_info.R")
source("scripts/summary_table.R")
source("scripts/women_in_stem.R")
source("scripts/employment_by_majors.R")
source("scripts/bar_chart.R")
```

### Midpoint Deliverable Report

Our domain of interest is about education, more specifically how level and field
of education, and gender affect salary. Our data set was imported from 
**fivethirtyeight** which based its data from the United States Census. The [data set](https://github.com/fivethirtyeight/data/tree/master/college-majors)
contains information pertaining to the salary, employment, and gender data 
of different majors and levels of education. 

### Summary Paragraph
```{r summary, include = FALSE, message = FALSE}
info <- get_summary_info(all_grad_data, grad_student_data)
info$highest_avg_unemployment_rate
info$lowest_avg_unemployment_rate
info$highest_median_salary
info$lowest_median_salary
info$grad_vs_nongrad
```
TEST `r info$highest_avg_unemployment_rate` AND THIS `r info$highest_median_salary`


### Summary Table
```{r kable, echo = FALSE, message = FALSE}
kable(displayed_table)
```

### Charts

#### Pie Chart

```{r, echo=FALSE, message = FALSE}
pie_women_majors
```

#### Bar Chart

```{r, echo=FALSE, message = FALSE, fig.width = 30, fig.height= 15}
chart_plot
```

#### WAGES chart

```{r, echo=FALSE, message = FALSE, fig.width = 10, fig.height= 5}
desc_employment_by_majors

scatter_plot
```

