---
title: "Education Project Midpoint Deliverable"
author: "Ian, Brenda, Leon, Jerry, Nicole"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("knitr")
library("dplyr")
library("plotly")
source("scripts/summary_info.R")
source("scripts/summary_table.R")
source("scripts/women_in_stem.R")
source("scripts/employment_by_majors.R")
source("scripts/bar_chart.R")
```

## How Level and Field of Education, as we

### Introduction

Our domain of interest is about education, more specifically how level and field
of education affect salary and the gender disparities between different fields. 
Our data set was imported from **fivethirtyeight** which based its data from the 
United States Census. The 
[data set](https://github.com/fivethirtyeight/data/tree/master/college-majors)
contains information pertaining to the salary, employment, and gender data 
of different majors and levels of education. 

### Summary Paragraph
```{r summary, include = FALSE, message = FALSE}
info <- get_summary_info(all_grad_data, grad_student_data)
info$highest_avg_unemployment_rate
info$lowest_avg_unemployment_rate
info$highest_median_salary
info$lowest_median_salary
info$grad_vs_nongrad
```

There were a total of 5 datasets provided from our source. **all-ages.csv**,
**grad-students.csv**, **recent-grads.csv**, **majors-list.csv**, and
**women-stem.csv**. The recent-grads dataset contains all information from
individuals **<28**, while grad-students contains all information from individuals
ages **25+**. Most of the data parsed was from the all-ages dataset. From the data
analysis we can conclude that the field with the highest unemployment rate is
**`r info$highest_avg_unemployment_rate`** while the field with the lowest 
unemployment rate is **`r info$lowest_avg_unemployment_rate`**. In addition, the
field with the highest median salary is **`r info$highest_median_salary`**, while 
the field with the lowest median salary is **`r info$lowest_median_salary`**. 
When comparing the median salary of students who had gone to grad school versus 
students who had not gone to grad school, the average difference was, 
**$`r format(info$grad_vs_nongrad, scientific = FALSE)`**.

### Summary Table
```{r kable, echo = FALSE, message = FALSE}
kable(displayed_table)
```

### Charts

#### Pie Chart

```{r, echo=FALSE, message = FALSE}
desc_chart_diff_majors

pie_women_majors
```

#### Bar Plot

```{r, echo=FALSE, message = FALSE}
chart_description

chart_plot
```

#### Scatter Plot

```{r, echo=FALSE, message = FALSE, fig.width = 10, fig.height= 8}
desc_employment_by_majors

scatter_plot
```

