---
title: "Education Project Midpoint Deliverable"
author: "Ian, Brenda, Leon, Jerry, Nicole"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("knitr")
library("dplyr")
library("plotly")
source("scripts/summary_info.R")
source("scripts/summary_table.R")
source("scripts/women_in_stem.R")
source("scripts/employment_by_majors.R")
source("scripts/wages_by_major.R")
```

## How Level and Field of Education affect salary, Gender disparities in Majors

### Introduction

The domain of interest of this project is about education, more specifically how level and field of education affect salary and the gender disparities between different fields. 
Our data set was imported from *fivethirtyeight* which based its data from the United States Census. The [data set](https://github.com/fivethirtyeight/data/tree/master/college-majors)
contains information pertaining to the salary, employment, and gender data 
of different majors and levels of education. 

### Summary Paragraph
```{r summary, include = FALSE, message = FALSE}
info <- get_summary_info(all_grad_data, grad_student_data)
info$highest_avg_unemployment_rate
info$lowest_avg_unemployment_rate
info$highest_median_salary
info$lowest_median_salary
info$grad_vs_nongrad
```

There were a total of 5 datasets provided from our source. *all-ages.csv*,
*grad-students.csv*, *recent-grads.csv*, *majors-list.csv*, and
*women-stem.csv*. The recent-grads dataset contains all information from
individuals **<28**, while grad-students contains all information from individuals ages **25+**. Most of the data parsed was from the all-ages dataset. From the data analysis we can conclude that the field with the highest unemployment rate is **`r info$highest_avg_unemployment_rate`** while the field with the lowestunemployment rate is **`r info$lowest_avg_unemployment_rate`**. In addition, the field with the highest median salary is **`r info$highest_median_salary`**, whilethe field with the lowest median salary is **`r info$lowest_median_salary`**. When comparing the median salary of students who had gone to grad school versus students who had not gone to grad school, the average difference was, **$`r format(info$grad_vs_nongrad, scientific = FALSE)`**.

### Summary Table

> The summary table is grouped by major category and display its *mean salary*, *25th Percentile Salary*, and *75th Percentile Salary*. The aggregate table obviously shows the numerical difference of these 3 values among various majors. 

```{r kable, echo = FALSE, message = FALSE}
kable(get_summary_table(grad_stu_df))
```

### Charts

#### Pie Chart

```{r, echo = FALSE, message = FALSE, fig.align="center"}
pie_women_majors
```

> This chart was intended to display the proportion of women in different the major categories of STEM.

#### Bar Plot

```{r, echo = FALSE, message = FALSE, fig.align="center"}
chart_plot
```

> The graph above arranges the different majors in categories and then calculates their average salary. It shows their wages from the hoghest to the lowest average pay.

#### Scatter Plot

```{r, echo = FALSE, message = FALSE, fig.width = 10, fig.height= 8}
scatter_plot
```

> This chart was intended to visualize the difference between employeed students and unemployeed by majors. The radius of each dot is a representation of the median salary by majors.
